Corticosteroids in HELLP syndrome

### 2023-10-26 data/synthesis copy.Rmd
Update

---
title: "Corticosteroids for improving patient relevant outcomes in HELLP syndrome"
subtitle: "Data synthesis script"
author: "Ashraf Nabhan"
output: html_document
date: "2023-09-26"
always_allow_html: true
---

@@

# PRISMA Flow diagram

```{r warning=FALSE}
cort = read.csv("cort.csv") 
cort = PRISMA_data(cort) 
pfd = PRISMA_flowdiagram(data = cort,other = F,previous = F,fontsize = 12)
pfd
```

@@

## Import dataset

## Pre-specified outcomes

@@

```{r}
rob2md = read.csv("rob2md.csv") 
rob_summary(data = rob2md,tool = "ROB2")
rob_traffic_light(data = rob2md,tool = "ROB2")
```

>>>>

---
title: "Corticosteroids in HELLP syndrome"
subtitle: Data and synthesis script
date: "2023-09-26"
output: html_document
always_allow_html: yes
---

@@

# Dataset

```{r}
kable(raw.data)
```

@@

**Pre-specified outcomes**

@@

Summary traffic-light plot of risk-of-bias assessments

```{r}
include_graphics("rob2.png")
```

Summary weighted barplot of risk-of-bias assessments

```{r}
include_graphics("rob_summary.png")
```
